---
title: "Module 12"
output: html_document
date: "2024-03-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Bookstuff

The first function in this package is bookFrame() which creates a dataframe named books_df with author, genre, and title as column names.

```{r bookframe}
bookFrame <- function() {
  books_df <- data.frame(
    author = character(),
    genre = character(),
    title = character(),
    stringsAsFactors = FALSE
  )
  assign("books_df", books_df, envir = .GlobalEnv)  # Store in the global environment
}

# Example

bookFrame()
books_df
```

## Adding books

The next function lets you add books to the dataframe. This function takes in 3 variables author, genre, and title and add that to the books_df data frame.

```{r pressure, echo=FALSE}
bookAdd <- function(author, genre, title) {
  # Create a new row with the book details
  new_book <- data.frame(author = author,
                         genre = genre,
                         title = title,
                         stringsAsFactors = FALSE)
  
  # Append the new book row to the existing data frame
  books_df <<- rbind(books_df, new_book)
  
  # Print the updated data frame
  print(books_df)
}

# Example
bookAdd('Gabrielle Zevin', 'Fiction','Tomorrow, and Tomorrow, and Tomorrow')
```




## Exporting books

The next function exports the dataframe as a .csv file named books.csv


```{r bookExport}

bookExport <- function() { 
  write.csv(books_df, 'books.csv', row.names = FALSE)
  
}

bookExport()

```
## Removing books

The last function lets you add remove books from the dataframe. This function takes in the title of the book and keeps everything in the dataframe that doesn't match the title

```{r bookRemove}
bookRemove <- function(title) {

    books_df <<- books_df[books_df$title != title, ]
    print(books_df)
  }

bookRemove('Tomorrow, and Tomorrow, and Tomorrow')
